### 2012-11-13 doc/progress_plan/report.tex
Added SAPIENTA paragraph

Liakata et al. (2012) describe a system for automatically processing and
categorising sentences in a research paper according to their respective
CoreSC.

>>>>

Liakata et al. (2012) describe a system for automatically processing and
categorising sentences in a research paper according to their respective
CoreSC element\cite{citeulike:10444769}. SAPIENTA
(\url({http://www.sapientaproject.com}) was trained using the ART corpus and
can achieve promising accuracies when categorising sentences \it{(Ibid)}. With
the authors' permissions, Partridge will make use of SAPIENTA when introducing
new papers into its repository. It is hoped that preclassifying papers will
make the development of Partridge more manageable within the timeframe
available and will also allow more effort to be put into other classification
problems rather than re-implementing a SAPIENTA clone. Any modifications that
have to be made to SAPIENTA to integrate it into Partridge will be submitted
back to the original authors to help them improve their works.
